SubsidyExplorer - Step 4: Apply proposal 'definitions' to vessel list

### 2020-09-15 scripts/05_subsidy_reform_definitions.Rmd
fixing normalize shipname

# Package to normalize vessel names in the same way GFW normalizes vessel names
#devtools::install_github("jcvdav/startR")
library(startR)

@@

```{r}
# Exclude intra EU fishing
distant_water_fishing <- distant_water_fishing %>%
  mutate(is_intra_EU = case_when(flag_iso3 %in% c(eu_countries, eu_northern_agreement) & eez_territory1_iso3 %in% c(eu_countries, eu_northern_agreement) ~ T,
                                 flag_sovereign_iso3 %in% c(eu_countries, eu_northern_agreement) & eez_territory1_iso3 %in% c(eu_countries, eu_northern_agreement) ~ T,
                                 TRUE ~ F)) %>%
  dplyr::filter(!is_intra_EU) %>%
  mutate(distant_water = T) %>%
  dplyr::select(eez_id, ssvid, fao_region, distant_water)
```

@@

```{r}
temp_vessel_list <- temp_vessel_list %>%
  left_join(distant_water_fishing, by = c("eez_id", "ssvid", "fao_region"))
temp_vessel_list$distant_water[is.na(temp_vessel_list$distant_water)] <- F

>>>>

# Package to normalize vessel names in the same way GFW normalizes vessel names
#devtools::install_github("jcvdav/startR")
#library(startR)
# This used to live in the startR package, but now lives locally - the package developer is currently having some difficulties related to the update to R version 4.0
source(here::here("scripts", "functions", "normalize.R"))
devtools::install_github("rich-iannone/UnidecodeR")
library(UnidecodeR)

@@

```{r}
# Exclude intra EU fishing
distant_water_fishing <- distant_water_fishing %>%
  mutate(is_intra_EU = case_when(flag_iso3 %in% c(eu_countries, eu_northern_agreement) & eez_territory1_iso3 %in% c(eu_countries, eu_northern_agreement) ~ T,
                                 flag_sovereign_iso3 %in% c(eu_countries, eu_northern_agreement) & eez_territory1_iso3 %in% c(eu_countries, eu_northern_agreement) ~ T,
                                 TRUE ~ F)) %>%
  dplyr::filter(!is_intra_EU) %>%
  mutate(distant_water = T) %>%
  dplyr::select(eez_id, ssvid, fao_region, is_territorial, distant_water)
```

@@

```{r}
temp_vessel_list <- temp_vessel_list %>%
  left_join(distant_water_fishing, by = c("eez_id", "ssvid", "fao_region", "is_territorial"))
temp_vessel_list$distant_water[is.na(temp_vessel_list$distant_water)] <- F
```
